SunPy - Python for Solar Physics

### 2014-01-27 2-2-Lightcurve.tex
edits to lightcurve section

\subsection{Lightcurve}

Time series data and analyses are a fundamental aspect of solar physics 
for which many data sources are available. 
In recognition of this fact, SunPy provides a \texttt{LightCurve} object 
designed to provide a convenient and consistent interface for handling 
solar time series data. 
The main engine behind the \texttt{LightCurve} object is the \texttt{pandas} 
data analysis library. 
This library contains a large amount of functionality for manipulating 
and analysing time series data, making it an ideal basis for 
\texttt{LightCurve}.  
Like all other SunPy objects, \texttt{LightCurve} is a wrapper around 
a data object, which in this case is the \texttt{pandas} object.

Currently, the \texttt{LightCurve} object is compatible with the following 
data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, 
and the SDO EUV Variability Experiment (EVE). 
For each of these instruments, a sub-class of the \texttt{LightCurve} object 
is initialised (e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits 
from \texttt{LightCurve} but allows instrument-specific functionality to be 
included. 
Future developments will introduce support for additional instruments and data 
products. 
Since time series data is generally relatively small and there is no 
established standard as to how it should be stored and distributed, 
each SunPy \texttt{LightCurve} object provides the ability to download 
its own data in its constructor.

>>>>

\subsection{Lightcurve}\label{sec:lightcurve}

Time series data and their analysis are a fundamental aspect of solar
physics for which many data sources are available.  In recognition of
this fact, SunPy provides a \texttt{LightCurve} object designed to
provide a convenient and consistent interface for handling solar time
series data.  The main engine behind the \texttt{LightCurve} object is
the \texttt{pandas} data analysis library (available at
\url{http://pandas.pydata.org}).  This library contains a large amount
of functionality for manipulating and analysing time series data,
making it an ideal basis for \texttt{LightCurve}.  Like other SunPy
objects, \texttt{LightCurve} is a wrapper around a data object, which
in this case is the \texttt{pandas} object.  \texttt{LightCurve}
assumes that the input data are time-ordered list(s) of numbers.  Each
list becomes a column in a \texttt{pandas} DataFrame object.

Currently, the \texttt{LightCurve} object is compatible with the
following data sources: the GOES X-ray Sensor (XRS), PROBA2/LYRA, and
the SDO EUV Variability Experiment (EVE; only the level ``OCS'' and
average CSV files - see \url{http://lasp.colorado.edu/home/eve/data/}
for more detail).  For each of these instruments, a sub-class of the
\texttt{LightCurve} object is initialised
(e.g. \texttt{GOESLightCurve, LYRALightCurve}) which inherits from
\texttt{LightCurve} but allows instrument-specific functionality to be
included.  Future developments will introduce support for additional
instruments and data products.  Since time series data is generally
relatively small and there is no established standard as to how it
should be stored and distributed, each SunPy \texttt{LightCurve}
object provides the ability to download its own data in its
constructor.
